Energy and the CES production function

### 2015-09-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Better graph name.

<<>>=
require(tidyr)
AllOE %>% 
  mutate(split =
           as.character(
             interaction(
               factor(flavor, labels = c("QA", "UA")), 
               factor(nest, 
                      labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
               sep = ", ",
               lex.order = FALSE ) )
  ) %>%
  gather(factor, elasticity, oe1, oe2, oe3) %>%
  mutate(
    split2 = relevelFactor(
      factor(split), 
      paste( rep(c("UA", "QA"), times = 4 ), 
             rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
             sep=", ")
    )
  ) %>%
  ggplot(aes(x=Year)) + 
  geom_line( 
    alpha = .8, # size=1.0,
    aes(y = elasticity, 
        colour = factor,
        linetype=factor,
        size = factor
    ) ) +
  facet_grid(split2 ~ Country) +
  scale_color_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c("black", "black", "gray70")
  ) +
  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
  scale_size_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values = c(.9, .9, .6)) +
  scale_linetype_manual( 
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c(2,3,1) ) + 
  xy_theme()

>>>>

<<Graphs_all_models_alphas_time, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="Output elasticity ($\\alpha$) for all models.">>=
require(tidyr)
AllOE %>% 
  mutate(split =
           as.character(
             interaction(
               factor(flavor, labels = c("QA", "UA")), 
               factor(nest, 
                      labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
               sep = ", ",
               lex.order = FALSE ) )
  ) %>%
  gather(factor, elasticity, oe1, oe2, oe3) %>%
  mutate(
    split2 = relevelFactor(
      factor(split), 
      paste( rep(c("UA", "QA"), times = 4 ), 
             rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
             sep=", ")
    )
  ) %>%
  ggplot(aes(x=Year)) + 
  geom_line( 
    alpha = .8, # size=1.0,
    aes(y = elasticity, 
        colour = factor,
        linetype=factor,
        size = factor
    ) ) +
  facet_grid(split2 ~ Country) +
  scale_color_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c("black", "black", "gray70")
  ) +
  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
  scale_size_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values = c(.9, .9, .6)) +
  scale_linetype_manual( 
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c(2,3,1) ) + 
  xy_theme()
